\TitlePt

### 2016-03-02 paper1.tex
Convert hrefs to explicit in text urls

The seismic method is among the most widely studied due to the high
industry demand. Thus, a range of well established open-source software
have been developed for seismic processing. These include
\href{http://www.cwp.mines.edu/cwpcodes/}{Seismic Un*x} (SU)
\citep{stockwelljr.1999},
\href{http://www.ahay.org/}{Madagascar} \citep{madagascardevelopmentteam2013},
\href{http://opendtect.org}{OpendTect}, and
\href{http://www.gebrproject.com}{GêBR}. A noteworthy open-source
project that is not seismic related is the
\href{http://gmt.soest.hawaii.edu/}{Generic Mapping Tools}
(GMT) project
\citet{wessel1991}. The GMT are a well established collection of command-line
programs for plotting maps with a variety of different map projections.
For geodynamic modeling there is the
\href{http://www.geodynamics.org}{Computational Infrastructure for
Geodynamics}, which has grouped various well documented software
packages. However, even with this wide range of well maintained software
projects, many geophysical modeling software that are provided online
still have no open-source license statement, have cryptic I/O files, are
hard to integrate into a pipeline, and make code reuse and remixing
challenging. Some of these problems are being worked on by the
\href{http://geosys.usc.edu/projects/seatree/}{Solid Earth Teaching and
Research Environment} (SEATREE) \citet{milner2009} by providing a common
graphical interface for previously existing software. The numerical
computations are performed by the pre-existing underlying C/Fortran
programs. Conversely, the SEATREE code (written in Python) handles the
I/O and user interface. This makes the use of these tools easier and
more approachable to students. However, the lack of a common API means
that the code for these programs cannot be easily combined to create new
modeling tools.

\href{http://www.fatiando.org}{Fatiando a Terra} aims at providing such an API
for geophysical modeling. Functions in the \texttt{fatiando} package use
compatible data and mesh formats so that the output of one modeling function
can be used as input for another. Furthermore, routines can be combined and
reused to create new modeling algorithms.  Fatiando a Terra also automates
common tasks such as griding, map plotting with
\href{http://matplotlib.org}{Matplotlib} \citep{hunter2007}, and 3D plotting
with \href{http://code.enthought.com/projects/mayavi}{Mayavi}
\citep{ramachandran2011}.  Version 0.1 of Fatiando a Terra is focused on
gravity and magnetic methods because this is the main focus of the developers.
However, simple ``toy'' problems for seismology and geothermics are available
and can be useful for teaching geophysics.

The following sections illustrate the functionality and design of
Fatiando a Terra using various code samples. An
\href{http://ipython.org/}{IPython} \citep{perez2007} notebook file with these
code samples is provided by \citet{uieda2013} at
\url{http://dx.doi.org/10.6084/m9.figshare.708390}.

@@

Map projections in Matplotlib are handled by the
\href{http://matplotlib.org/basemap}{Basemap toolkit}. The
\texttt{fatiando.vis.mpl} module also provides helper functions to
automate the use of this toolkit. The \texttt{fatiando.vis.mpl.basemap}
function automates the creation of the \texttt{Basemap} objects with
common parameters. This object can then be passed to the
\texttt{contourf}, \texttt{contour} and \texttt{pcolor} functions in
\texttt{fatiando.vis.mpl} and they will automatically plot using the
given projection (Figure~\ref{fig:p1-basemap}):

>>>>

The seismic method is among the most widely studied due to the high industry
demand. Thus, a range of well established open-source software have been
developed for seismic processing. These include Seismic Un*x \citep[][
\url{http://www.cwp.mines.edu/cwpcodes/}]{stockwelljr.1999}, Madagascar
\citep[][ \url{http://www.ahay.org/}]{madagascardevelopmentteam2013}, OpendTect
(\url{http://opendtect.org}), and GêBR (\url{http://www.gebrproject.com}). A
noteworthy open-source project that is not seismic related is the Generic
Mapping Tools (GMT) project \citep[][
\url{http://gmt.soest.hawaii.edu/}]{wessel1991}. The GMT are a well established
collection of command-line programs for plotting maps with a variety of
different map projections.  For geodynamic modeling there is the Computational
Infrastructure for Geodynamics (\url{http://www.geodynamics.org}), which has
grouped various well documented software packages. However, even with this wide
range of well maintained software projects, many geophysical modeling software
that are provided online still have no open-source license statement, have
cryptic I/O files, are hard to integrate into a pipeline, and make code reuse
and remixing challenging. Some of these problems are being worked on by the
Solid Earth Teaching and Research Environment (SEATREE) \citep[][
\url{http://geosys.usc.edu/projects/seatree/}]{milner2009} by providing a
common graphical interface for previously existing software. The numerical
computations are performed by the pre-existing underlying C/Fortran programs.
Conversely, the SEATREE code (written in Python) handles the I/O and user
interface. This makes the use of these tools easier and more approachable to
students. However, the lack of a common API means that the code for these
programs cannot be easily combined to create new modeling tools.

Fatiando a Terra (\url{http://www.fatiando.org}) aims at providing such an API
for geophysical modeling. Functions in the \texttt{fatiando} package use
compatible data and mesh formats so that the output of one modeling function
can be used as input for another. Furthermore, routines can be combined and
reused to create new modeling algorithms.  Fatiando a Terra also automates
common tasks such as griding, map plotting with Matplotlib \citep[][
\url{http://matplotlib.org}]{hunter2007}, and 3D plotting with Mayavi \citep[][
\url{http://code.enthought.com/projects/mayavi}]{ramachandran2011}.  Version
0.1 of Fatiando a Terra is focused on gravity and magnetic methods because this
is the main focus of the developers.  However, simple ``toy'' problems for
seismology and geothermics are available and can be useful for teaching
geophysics.

The following sections illustrate the functionality and design of Fatiando a
Terra using various code samples. An IPython \citep[][
\url{http://ipython.org/}]{perez2007} notebook file with these code samples is
provided by \citet{uieda2013} at
\url{http://dx.doi.org/10.6084/m9.figshare.708390}.

@@

Map projections in Matplotlib are handled by the
Basemap toolkit (\url{http://matplotlib.org/basemap}). The
\texttt{fatiando.vis.mpl} module also provides helper functions to
automate the use of this toolkit. The \texttt{fatiando.vis.mpl.basemap}
function automates the creation of the \texttt{Basemap} objects with
common parameters. This object can then be passed to the
\texttt{contourf}, \texttt{contour} and \texttt{pcolor} functions in
\texttt{fatiando.vis.mpl} and they will automatically plot using the
given projection (Figure~\ref{fig:p1-basemap}):
